\section{Roadmap}
Our roadmap is divided into two parallel tracks, one for the development of ESB and the other for the ongoing enhancement of USB.

\subsection{ESB: The MiCA-Compliant Euro Stablecoin}
\begin{itemize}
    \item \textbf{Q3 2025}: Finalize legal and regulatory framework for ESB and submit application for ART license under MiCA.
    \item \textbf{Q4 2025}: Launch private beta for ESB with a select group of institutional partners.
    \item \textbf{Q1 2026}: Launch public beta for ESB and begin integration with European payment providers.
    \item \textbf{Q2 2026}: Full public launch of ESB and expansion of the ESB rewards program.
\end{itemize}

\subsection{USB: The Decentralized International Stablecoin}
\begin{itemize}
    \item \textbf{Q3 2025}: Launch USB on additional decentralized exchanges and expand liquidity mining programs.
    \item \textbf{Q4 2025}: Integrate USB with additional DeFi protocols for lending, borrowing, and yield farming.
    \item \textbf{Q1 2026}: Expand the USB hedging strategy to include additional crypto-assets, further enhancing its stability and yield.
    \item \textbf{Q2 2026}: Launch a user-friendly interface for minting, redeeming, and staking USB.
\end{itemize}

\subsection{SBL: The Unified Governance Token}
\begin{itemize}
    \item \textbf{Q3 2025}: Launch the SBL governance portal, allowing token holders to vote on key protocol parameters.
    \item \textbf{Q4 2025}: Transition to a fully decentralized autonomous organization (DAO) governed by SBL holders.
\end{itemize}  