%----------------------------------------------------------------------------------------
% Introduction
%----------------------------------------------------------------------------------------
\setcounter{page}{1} % Sets counter of page to 1
\section{Introduction}
Stabolut is pioneering a dual-stablecoin strategy to address the diverse needs of the global digital economy. Our ecosystem features two distinct stablecoins: ESB, a Euro-pegged, MiCA-compliant Asset-Referenced Token (ART) for the European market, and USB, a US Dollar-pegged, decentralized stablecoin for international markets.

\subsection{ESB: The MiCA-Compliant Euro Stablecoin}
ESB is designed to be a fully regulated and transparent stablecoin for the European Union. It is pegged to the Euro and backed by a reserve of high-quality liquid assets, in strict compliance with MiCA regulations. While ESB does not offer a direct yield, it provides value to users through a sophisticated system of transaction-based rewards, loyalty programs, and other MiCA-compliant incentives.

\subsection{USB: The Decentralized International Stablecoin}
USB is a decentralized, US Dollar-pegged stablecoin designed for the global DeFi market. It is backed by a basket of crypto assets and utilizes a sophisticated hedging mechanism to maintain its peg. USB is a yield-bearing token, offering a competitive return to holders in jurisdictions where such products are permitted.

\subsection{The SBL Governance Token}
The entire Stabolut ecosystem is governed by the SBL token. SBL holders have the power to vote on key parameters for both ESB and USB, including risk management, treasury allocation, and the implementation of new features. This ensures that the Stabolut protocol remains a community-driven and decentralized project.

This whitepaper provides a comprehensive overview of the Stabolut ecosystem, detailing the architecture, mechanisms, and tokenomics of ESB, USB, and SBL.
